My title

### 2024-12-02 paper/paper.qmd
Finished the first total draft of the paper.
Finished the first total draft of the paper. Included the Appendix, Reference, Result and the Discussion part.

library(tidyverse)
library(rstanarm)
library(knitr)
library(kableExtra)
library(modelsummary)
library(scales)
library(here)
library(readr)
library(arrow)

@@

Overview paragraph

@@

# Data {#sec-data}
We used the R programming language [@citeR] to analyze the data and plot the graphs for this paper. The folder structure for this paper follows the startup folder created by [@rohan]. It is very helpful in keeping everything organized. I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively. In addition, the `tidyverse` [@citetidyverse] packages are essential for simplifying data cleaning and analysis.`styler` [@citestyler] is used in arranging code style. These tools help to organize and present data efficiently. I also plotted the graphs with `ggplot2` [@citeggplot2] and read the CSV file with `here` [@citehere]. We also use the `comma` function from the `scales` [@citescales] library to format the data, thereby avoiding scientific notation in our charts. We used the `knitr` [@citeknitr] to show the table.

@@

The dataset used for this analysis originates from the Toronto Police Service's public data [@TorontoPoliceData]. It aims to promote transparency and allow the public to analyze and understand various types of crime in Toronto. The dataset provides comprehensive records of bike theft incidents reported across different regions of the city. It serves as a valuable resource for analyzing trends and developing preventive strategies to combat bike theft. In addition to the Toronto Police Service's bicycle theft dataset, other Canadian cities and countries provide similar data. For example, the Ottawa Police Service offers a dataset detailing bicycle theft occurrences from 2015 to 2020. But this dataset is limited to Ottawa and may not reflect the unique patterns and trends present in Toronto, which means there were no similar datasets that could have been used in this research.

@@

The raw dataset provides 35 varibles with 37178 obeservations related to the incidents of bike theft, capturing various aspects of each theft that are crucial for understanding patterns and determining effective measures. The variables that I chose from the whole dataset is `STATUS`, `OCC_MONTH`, `OCC_HOUR`, `NEIGHBOURHOOD_158`, `PREMISES_TYPE`, `BIKE_COST`. However, using these variables directly makes analyzing more difficult. For example, the original data of `OCC_MONTH` was recorded as month names (in its character form, like "January"), which would complicate temporal analysis. Also, the `NEIGHBOURHOOD_158` included a large amount of neighborhoods' name, making it difficult to derive meaningful and useful insights from the neighborhood data.

After simply understand the raw data, the next step was data cleaning and to transform it into a more suitable format for analysis. The first action involved renaming key variables for better clarity and consistency, ensuring that each variable was descriptive and aligned with the analysis goals.
The renaming and explanation of each varible included in the following:

- `Occurrence_Hour`(`OCC_HOUR`): The hour of the day (0-23) when the theft occurred.
- `Premises_Type`(`PREMISES_TYPE`): The type of location where the theft took place (e.g., residential, commercial).
- `Bike Cost`(`BIKE_COST`): The reported monetary value of the stolen bicycle.

Further specially state:

`OCC_MONTH` variable was originally recorded as month names (e.g., January, February). It was converted into numeric format `Occurrence_Month`, with each month represented by an integer from 1 to 12 (e.g., January = 1, February = 2).
`STATUS` was converted to a binary variable named `Theft_Status` to simplify analysis by distinguishing whether a theft occurred (1) or not (0) and for further model analysis
`NEIGHBOURHOOD_158` was converted to `Region`. According to the `neighbourhood_mapping`, the neighborhood data was grouped into broader regions (e.g., Downtown, Midtown, Scarborough) to simplify the analysis. Each neighborhood was mapped to a major region based on its geographic location.

The remaining modified variables are explained in the following:

- `Occurrence_Month`(`OCC_MONTH`): The month in which the bicycle theft occurred.
- `Theft Status`(`STATUS`): Indicates whether the reported bicycle theft occurred or other(e.g., unfound, recovery). (1 = stolen, 0 = Other).
- `Region`(`NEIGHBOURHOOD_158`): The broader geographical area where the theft occurred, grouped from specific neighborhood names (e.g., Downtown, Midtown, Scarborough).

@@

@@

# Select the first 10 rows
preview_table <- head(analysis_data, 10)

```{r}
#| label: tbl-data-summary
#| tbl-cap: "Summary Statistics of Cleaned Bike Theft Data"
#| echo: false
#| warning: false
#| message: false
#| 
# Calculate summary statistics for numeric and categorical columns
summary_stats <- datasummary_skim( 
  histogram = FALSE,
  analysis_data, 
  output = "data.frame"  # Ensure the output is in data frame format
)

@@

```
The summary statistics in @tbl-data-summary show key insights about the cleaned bike theft data. The variable "Theft_Status" has only two unique values, with a mean of 1.0, indicating that the majority of bikes were stolen, as the variable is binary (0 or 1). "Occurrence_Hour" has a mean value of 13.4, suggesting that bike thefts tend to happen during afternoon hours, and it has values ranging from 0 to 23, representing all hours of the day. The "Occurrence_Month" variable has 12 unique values, covering the entire year, with an average value of 7, indicating more thefts occurring around mid-year. The average bike cost is around 679.9, with a wide variation from 0 to 2034, showing the diverse range of bikes affected.

@@

Once a report is submitted, it is reviewed by the appropriate authorities and, if verified, the incident becomes an entry in the dataset used for analysis. Each entry in the dataset corresponds to a real-world burglary event and includes attributes such as when the burglary occurred, the type of premises (e.g., residential, commercial), and the neighborhood or district. These attributes help to understand the context of each burglary and allow for further analysis to identify burglary patterns or high-risk areas.

@@

```{r}
#| label: fig-month-type-status
#| fig-cap: "Seasonal Patterns of Bicycle Theft Across Different Premises Types"
#| echo: false
#| warning: false
#| message: false

# Create a bar chart for the cleaned data
analysis_data %>% 
  filter(!is.na(Occurrence_Month)) %>%
  ggplot(aes(x = Occurrence_Month, fill = factor(Theft_Status))) + 
    geom_bar(stat = "count") +
    scale_fill_brewer(palette = "Set1", labels = c("Other", "Stolen")) + 
    labs(
      x = "Month", 
      y = "Number of Incidents", 
      fill = "Theft Status"
    ) +
    facet_grid(~ Premises_Type) +
    theme_bw() +
    theme(
      legend.position = "bottom",
      legend.text = element_text(size = 8), 
      legend.title = element_text(size = 10), 
      legend.key.size = unit(1.3, "lines"),
      panel.grid.major = element_line(color = "gray80"),
      panel.grid.minor = element_blank(), 
      legend.background = element_rect(fill = "white", colour = "black"),
      axis.text.x = element_text(size = 7.5)
    )
```
@fig-month-type-status provides a month-by-month breakdown of bicycle theft incidents in different types of premises and is colored according to the status of each incident. The bar chart clearly shows that thefts tend to peak in the warmer months, a trend that can be attributed to increased bicycle usage. A closer look at the chart reveals that a large percentage of cases remain unsolved (Status = Stolen), while only a small portion of cases are in unknown or recovered status (Status = Other). In addition, locations such as “Outdoors” areas and “Other” have a particularly high number of bicycle thefts, suggesting that these locations are more likely to have bicycle thefts compared to other locations.

```{r}
#| label: fig-hour
#| fig-cap: "Hourly Distribution of Bike Thefts"
#| echo: false
#| warning: false
#| message: false

ggplot(analysis_data, aes(x =Occurrence_Hour, fill = as.factor(Theft_Status))) +
  geom_histogram(binwidth = 1, position = "dodge") +
  labs(title = "Hourly Distribution of Bike Thefts",
       x = "Hour of Day",
       y = "Count of Thefts",
       fill = "Theft Status") +
  theme_minimal()

```
@fig-hour presents the frequency of bike thefts by hour throughout the day, categorized by theft status. Two colors distinguish the theft statuses: teal for stolen bikes (Theft Status = 1) and red for other statuses (Theft Status = 0). This visualization shows that theft incidents peak during the late evening hours, particularly around 18:00 to 23:00, suggesting a higher risk of bike theft during these hours. The lowest incidence of thefts tends to occur in the early morning hours, from midnight to early morning.

```{r}
#| label: fig-bike-cost
#| fig-cap: "Distribution of Stolen Bicycle Costs"
#| echo: false
#| warning: false
#| message: false
#| 
ggplot(analysis_data, aes(x = Bike_Cost)) +
  geom_histogram(bins = 30, fill = "lightblue", color = "black") +
  labs(
    x = "Bike Cost",
    y = "Frequency"
  ) +
  theme_minimal()

```
@fig-bike-cost shows the distribution of bike costs for bicycles reported as stolen. We can see that the majority of stolen bikes fall in the lower to mid-range price categories, with a concentration around $200 to $800. There are also a few bikes with higher values, indicating that expensive bikes, though stolen less frequently, are still targets. This distribution suggests that thieves generally target moderately priced bikes, likely because they are more common and potentially easier to steal.

@@

Occurrence hour captures the time of day the bike theft incident occurred, ranging from 0 to 23. Certain hours may be more prone to thefts due to lower public visibility or peak criminal activity times. Occurrence month reflects the month when the theft took place, from 1 (January) to 12 (December). Seasonal variations could affect theft rates, with possibly higher incidents in warmer months when bikes are more frequently used and accessible. Premises type categorized into "Residential," "Outdoors," and "Other," this variable helps in understanding the influence of location on theft probability. "Residential" includes places like apartments and houses, "Outdoors" covers areas such as educational, commercial, and transit, and "Other" encompasses miscellaneous or less common locations that do not fit into the first two categories. Different locations may have varying risks associated with bike theft, influenced by factors like population density, surveillance, and accessibility. Bike cost is a continuous variable represents the monetary value of the bike, under the premise that more expensive bikes might be more attractive targets for thieves due to their higher resale value.

@@

Here's the revised description for your Bayesian logistic regression model where "Apartment" is specified as the baseline category for the premises type variable:

@@

@@

@fig-ppcheck compares the observed data ($y$) with the replicated data generated by the Bayesian logistic regression model ($y_{rep}$). The alignment between the observed and replicated values indicates that the model reasonably captures the overall pattern of theft occurrences. However, minor deviations at lower probabilities highlight areas where the model's fit could be improved, suggesting potential limitations in capturing the little difference of the data.

@fig-trace-plot visualizes the Markov Chain Monte Carlo (MCMC) sampling for each parameter in the Bayesian logistic regression model across four chains. It shows consistent mixing and convergence, as indicated by the overlapping and steady oscillations of the chains within a stable range. For parameters such as the coefficient of occurrence hour and occurrence month, the chains demonstrate good mixing, suggesting that the model has adequately explored the parameter space. Similarly, for the coefficients for variables "premises type: outdoors" and "premises type: residential," the chains are stable, indicating reliable sampling. The absence of divergent transitions or extreme fluctuations across all parameters confirms the MCMC algorithm's proper functioning, implying that the posterior estimates are credible and the model is well-calibrated.

@fig-rhat displays the diagnostic, which assesses the convergence of Markov Chain Monte Carlo (MCMC) simulations for each parameter in the Bayesian logistic regression model. All $\hat{R}$ values are clustered around 1.00 and well below the critical thresholds of 1.05 or 1.1, indicating strong convergence across all parameters. This suggests that the multiple chains have mixed well and the posterior distributions are reliably estimated. As a result, the model's output can be trusted for further inference and analysis

@@

For location-based predictors, thefts are significantly more likely to occur at Outdoor Premises with an OR of 1.51, and a credible interval from 1.01 to 2.26, indicating a clear increase in risk compared to other premises. Conversely, Residential Premises show an OR of 0.96, with a credible interval of 0.71 to 1.31, suggesting a slightly lower likelihood of thefts at these locations relative to others.

The influence of Bike Cost per $1000 increase on theft likelihood is relatively neutral, with an OR nearly at 1 (0.99) and a credible interval between 0.78 and 1.27, indicating that the bike's cost does not significantly alter the odds of it being stolen.

@@

@tbl-modelsummary-results provides insights into the factors influencing bike theft occurrences based on the Bayesian logistic regression model. Overall, premises type emerges as a significant determinant of theft likelihood. Bikes parked in commercial and outdoor settings show a lower risk of theft, while educational premises indicate a potential increase in risk, though the precision of this estimate is lower. Temporal factors, such as the occurrence hour and month, have minimal impact on predicting theft occurrences. The model suggests that where a bike is parked is more crucial in determining theft risk than when it is parked.

```{r}
#| label: fig-credibility-interval
#| fig-cap: "Credible Interval of Bike Theft"
#| eval: true
#| echo: false
#| warning: false
#| message: false

library(ggplot2)
library(rstanarm)

# Extract posterior samples from the model
posterior_samples <- as.matrix(Bike_Theft_model)
posterior_samples[, "Bike_Cost"] <- posterior_samples[, "Bike_Cost"]*1000

# Compute odds ratios and their 95% credible intervals
credible_intervals <- data.frame(
  Variable = colnames(posterior_samples),                           # Predictor names
  OR = apply(posterior_samples, 2, function(x) exp(mean(x))),       # Exponentiate posterior means
  Lower = apply(posterior_samples, 2, function(x) exp(quantile(x, 0.025))), # 2.5% quantile
  Upper = apply(posterior_samples, 2, function(x) exp(quantile(x, 0.975)))  # 97.5% quantile
)
credible_intervals <- credible_intervals %>% filter(Variable != "(Intercept)")
# Filter out irrelevant variables (e.g., log-posterior, mean_PPD)
credible_intervals <- credible_intervals[!credible_intervals$Variable %in% c("mean_PPD", "log-posterior"), ]

# Clean variable names for better readability
credible_intervals$Variable <- recode(credible_intervals$Variable,
  "Occurrence_Hour" = "Hour of Occurrence",
  "Occurrence_Month" = "Month of Occurrence",
  "Premises_TypeOutdoors" = "Outdoor Premises",
  "Premises_TypeResidential" = "Residential Premises",
  "Bike_Cost" = "Bike Cost"
)

# Plot odds ratios with 95% credible intervals
ggplot(credible_intervals, aes(x = OR, y = Variable)) +
  geom_point(size = 3, color = "blue") +                              # OR as points
  geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2, color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +    # Reference line at OR = 1
  labs(
    title = "95% Credible Intervals for Odds Ratios",
    x = "Odds Ratio (OR)",
    y = NULL
  ) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 10))

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

>>>>

library(tidyverse)
library(rstanarm)
library(knitr)
library(kableExtra)
library(modelsummary)
library(here)
library(readr)
library(arrow)
library(bayesplot)
library(ggplot2)
library(styler)
```

@@

Overview paragraph 这里 google scholar 找3 篇文献 正文中引用，然后 文献 pdf 放 other 里的 literature 文件夹

@@

# Data {#sec-data}
We used the R programming language [@citeR] to analyze the data and plot the graphs for this paper. The folder structure for this paper follows the starter folder created by [@rohan]. I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively. In addition, the `tidyverse` [@citetidyverse] packages are essential for simplifying data cleaning and analysis.`styler` [@citestyler] is used in arranging code style. I also plotted the graphs with `ggplot2` [@citeggplot2] and read the CSV file with `here` [@citehere]. We used the `knitr` [@citeknitr] to show the table.The `rstanarm` package [@citerstanarm] allowed us to fit Bayesian regression models using Hamiltonian Monte Carlo. For improving the appearance and functionality of our tables, we employed the `kableExtra` package [@citekableExtra]. Data import and processing were facilitated by the `readr` package [@citereadr] for fast and efficient reading of tabular data, and the `arrow` package [@citearrow] for reading and writing data in various formats including Parquet. The `modelsummary` package [@citemodelsummary] provided tools to summarize and present regression model outputs in a convenient and customizable way. Visualizations of Bayesian models were created using the `bayesplot` package [@citebayesplot] and `styler` [@citestyler] used in arranging code style.

@@

The dataset used for this analysis originates from the Toronto Police Service's public data [@TorontoPoliceData]. It tries to promote transparency and allow the public to analyze and understand various types of crime in Toronto. The dataset provides comprehensive records of bike theft incidents reported across different regions of the city. It serves as a valuable resource for analyzing trends and developing preventive strategies to combat bike theft. In addition to the Toronto Police Service's bicycle theft dataset, other Canadian cities and countries provide similar data. For example, the Ottawa Police Service offers a dataset detailing bicycle theft occurrences from 2015 to 2020. But this dataset is limited to Ottawa and may not reflect the unique patterns and trends present in Toronto, which means there were no similar datasets that could have been used in this research.

@@

The initial raw dataset comprises 35 variables across 37,178 observations, detailing various aspects of bicycle theft incidents. This extensive collection includes data pivotal for discerning theft patterns and devising preventative strategies. Key variables were selected for their relevance and were initially presented in a format not conducive to straightforward analysis. For instance, time data was originally recorded as month names like "January," which complicates temporal analysis due to its non-numeric format.

To refine the dataset for more effective analysis, the initial step involved a thorough data cleaning process. This process included renaming key variables to ensure clarity and consistency across the dataset, making each variable's purpose clear and directly aligned with the objectives of the analysis. Moreover, the original premises type data was varied and broad, leading to diluted analytical outcomes when examining location-specific trends. To address this, less frequent categories such as Educational, Commercial, and Transit locations were consolidated under a singular 'Other' category. This regrouping allowed for a more focused analysis on prominent categories—Apartment, House, and Outdoors—each treated as distinct groups. This restructuring was crucial for achieving a more targeted and meaningful interpretation of the data, allowing for a clearer understanding of theft patterns by location type. To more clearly display and understand the analysis data, @tbl-cleaned-data is a preview of the cleaned data table.(see Appendix @sec-data-details)

The explanation of each cleaned variable with definition included in the following:

@@

To more clearly display and understand the analysis data, @tbl-cleaned-data is a preview of the cleaned data table.

```{r}
#| label: tbl-data-summary
#| tbl-cap: "Summary Statistics of Cleaned Bike Theft Data"
#| echo: false
#| warning: false
#| message: false

@@

# Calculate summary statistics for numeric and categorical columns
summary_stats <- datasummary_skim( 
  histogram = FALSE,
  analysis_data, 
  output = "data.frame"  # Ensure the output is in data frame format
)

@@

```
The summary statistics in @tbl-data-summary show key insights about the cleaned bike theft data. The variable 'Theft Status' has only two unique values, with a mean of 1.0, indicating that the majority of bikes were stolen, as the variable is binary (0 or 1). 'Occurrence Hour' has a mean value of 13.4, suggesting that bike thefts tend to happen during afternoon hours, and it has values ranging from 0 to 23, representing all hours of the day. The 'Occurrence Month' variable has 12 unique values, covering the entire year, with an average value of 7, indicating more thefts occurring around mid-year. The average bike cost is around 715.1, with a wide variation from 0 to 2330, showing the diverse range of bikes affected.

@@

Once a report is submitted, it is reviewed by the appropriate authorities and, if verified, the incident becomes an entry in the dataset used for analysis. Researchers can then analyze this data to identify patterns and trends, examining variables such as time of theft and location types. This methodical approach effectively links real-world theft events with their analytical representations, enabling a thorough examination of the dynamics and risk factors tied to different locations and premises within the dataset. This structured data transformation process is essential for generating insights into bicycle theft, providing a foundation for strategies to mitigate these incidents effectively. These attributes help to understand the context of each burglary and allow for further analysis to identify burglary patterns or high-risk areas.

@@

```{r}
#| label: fig-month-premises-type-status
#| fig-cap: "Seasonal Patterns of Bicycle Theft Across Different Premises Types"
#| echo: false
#| warning: false
#| message: false
#| 
# Create a bar chart for the cleaned data
analysis_data %>% 
  filter(!is.na(Occurrence_Month)) %>%
  ggplot(aes(x = Occurrence_Month, fill = factor(Theft_Status))) + 
    geom_bar(stat = "count") +
    scale_fill_brewer(palette = "Set1", labels = c("Other", "Stolen")) + 
    labs(
      x = "Month", 
      y = "Number of Incidents", 
      fill = "Theft Status"
    ) +
    facet_grid(~ Premises_Type) +
    theme_bw() +
    theme(
      legend.position = "bottom",
      legend.text = element_text(size = 8), 
      legend.title = element_text(size = 10), 
      legend.key.size = unit(1.3, "lines"),
      panel.grid.major = element_line(color = "gray80"),
      panel.grid.minor = element_blank(), 
      legend.background = element_rect(fill = "white", colour = "black"),
      axis.text.x = element_text(size = 7.5)
    )
```
@fig-month-premises-type-status provides a detailed month-by-month breakdown of bicycle theft incidents across various premises, categorized by theft status. It reveals a clear seasonal trend, with thefts peaking during the warmer months, likely due to increased bicycle usage. The data show that a vast majority of incidents are classified as 'Stolen', suggesting most cases remain unresolved, with few bicycles with the status 'unknown' and 'recovered'. Notably, locations categorized as 'Outdoors' and 'Other' record higher theft frequencies, indicating these are more vulnerable to theft. This analysis is important for making the effective theft prevention strategies, such as enhancing security measures and increasing surveillance during peak periods, to mitigate theft risks in identified hotspots.

```{r}
#| label: fig-hour-bike-thefts
#| fig-cap: "Time-Specific Patterns in Bike Thefts: Hourly Distribution Analysis"
#| echo: false
#| warning: false
#| message: false

ggplot(analysis_data, aes(x = Occurrence_Hour, fill = as.factor(Theft_Status))) +
  geom_histogram(binwidth = 1, position = "dodge") +
  labs(x = "Hour of Day",
       y = "Count of Thefts",
       fill = "Theft Status") +
  scale_fill_manual(values = c("0" = "red", "1" = "#377EB8")) + # Adjust the colors here
  theme_minimal()

@fig-hour-bike-thefts shows the frequency of bike thefts categorized by hour of the day and delineated by theft status. It uses two colors to represent different statuses: blue for confirmed stolen bikes (Theft Status = 1) and red for bikes that were either recovered or not confirmed as stolen (Theft Status = 0). The data show a notable increase in theft occurrences during the late evening, peaking between 18:00 and 23:00, which underscores a heightened risk of theft during these hours. Conversely, the early morning hours from midnight onwards display the lowest frequencies of theft, indicating minimal activity. This pattern suggests that preventative measures, such as enhanced security or surveillance, could be most effectively targeted during the evening hours to mitigate the risk of bike theft.

```{r}
#| label: fig-bike-cost-distribution
#| fig-cap: "Distribution of Stolen Bicycle Costs"
#| echo: false
#| warning: false
#| message: false
#| 
ggplot(analysis_data, aes(x = Bike_Cost)) +
  geom_histogram(bins = 30, fill = "#377EB8", color = "black") +
  labs(
    x = "Bike Cost",
    y = "Frequency"
  ) +
  theme_minimal()
```

@fig-bike-cost-distribution illustrates the frequency of bicycle thefts at various price points. The histogram shows a prominent peak in thefts for bikes priced between $200 and $800, highlighting that moderately priced bicycles are the most frequent targets. This is potentially due to their prevalence and easier resale value compared to high-priced bicycles, which, although targeted less frequently, still represent a significant portion of thefts. The chart provides insight into thief preferences and suggests that increased security measures may be particularly necessary for bikes within this price range to mitigate theft risks.

@@

The predictor variables for this analysis are thoughtfully selected to address various factors that might influence bike theft probability. 'Occurrence Hour' tracks the time of day the theft occurs, ranging from 0 to 23, to identify potential high-risk hours often associated with decreased public visibility and peak criminal activities. 'Occurrence Month' captures the month of the theft from January to December, reflecting seasonal variations that may see increases during warmer months when bicycles are used more frequently. 'Premises Type' is divided into "House," "Apartment," "Outdoors," and "Other." This categorization helps determine how different locations influence theft risks, with residential areas like houses and apartments generally being more secure, while public spaces categorized under "Outdoors" are more vulnerable. "Other" includes various non-standard locations such as educational and commercial areas, each carrying distinct security challenges. 'Bike Cost', as a continuous variable, represents the value of the bike, positing that more expensive bikes might be targeted more frequently due to their higher resale value. This comprehensive approach aims to uncover patterns and insights to help develop effective theft prevention strategies tailored to specific environmental and temporal factors.

@@

@@

Model comparison indicates that both the Bayesian logistic regression model and the frequentist logistic regression model achieved identical accuracy scores of 98.57% on the test dataset. This high accuracy suggests that both models effectively captured the relationship between the predictor variables (e.g., Occurrence_Hour, Occurrence_Month, Premises_Type, Bike_Cost) and the binary outcome (Theft_Status). The process of comparing these models involved splitting the dataset into training (80%) and testing (20%) subsets to evaluate their predictive performance on unseen data. Both models were trained on the training set, with their predictions compared against the actual values in the test set. Classifications were made using a threshold of 0.5 for predicted probabilities, and accuracy was computed as the proportion of correctly classified cases. These results demonstrate that both modeling approaches are highly effective for this particular dataset, yielding near-identical predictive performance.

While both the Bayesian and frequentist logistic regression models achieved identical accuracy scores, the Bayesian approach offers several advantages that make it particularly valuable. Bayesian models provide a probabilistic framework that incorporates prior knowledge into the analysis, allowing for more informed and interpretable results. For example, priors can regularize estimates, particularly in cases where the dataset is small or certain predictors are sparse, reducing the risk of overfitting. Additionally, Bayesian models generate full posterior distributions for parameter estimates, rather than single point estimates, which offers richer insights into the uncertainty and variability of the parameters. This is especially beneficial for decision-making processes that rely on quantifying uncertainty, as it provides credible intervals rather than just confidence intervals, which are more interpretable in probabilistic terms. Thus, even though the predictive performance of both models is comparable in this instance, the Bayesian approach offers additional interpretative benefits and robustness, particularly in scenarios with limited or uncertain data.

@@

@fig-ppcheck shows a posterior predictive check, which is a crucial diagnostic tool in Bayesian analysis used to compare the data observed in the real world ($y$) with data simulated from the model ($y_{rep}$). This comparison is fundamental for assessing whether the Bayesian logistic regression model is accurately capturing the underlying patterns of theft occurrences. In this analysis, the general alignment between the observed and replicated values across most of the probability range suggests that the model adequately captures the central trend of theft occurrences. This implies that the model's assumptions and the chosen priors are appropriate for the bulk of the data, providing a reasonable foundation for making inferences or predictions based on the model. However, the graph also shows minor deviations, particularly noticeable at higher probability values. These deviations signal areas where the model could be further refined. Such discrepancies might indicate that the model does not fully account for all nuances in the data, possibly due to oversimplified assumptions or constraints that fail to capture less frequent but plausible outcomes.

@fig-trace-plot provides a detailed visualization of the Markov Chain Monte Carlo (MCMC) sampling for various parameters in the Bayesian logistic regression model that tries to predict bike theft incidents. Each subplot specifically demonstrates the trace of sampled values across thousands of iterations for key model parameters: the intercept, hourly occurrence, monthly occurrence, premises type, and bike cost. These trace plots are essential for evaluating the convergence of the chains and the thoroughness with which the sampling process explores the posterior distributions of the parameters.The trace plots for 'Hourly Occurrence' and 'Monthly Occurrence' reveal the dynamic influence of time on the likelihood of bike thefts, showing fluctuations that suggest possible patterns or anomalies in theft occurrence throughout different hours of the day and months of the year. The plots for 'Outdoor Premises', 'Residential Premises', and 'Bike Cost' reflect on how each of these variables potentially alters the risk of theft, with the trace lines providing insight into the stability and significance of their effects within the model.

In Bayesian analysis, the quality of parameter estimation is gauged by the degree of overlap and the density of the trace lines across multiple chains. Here, the dense and intertwined nature of the traces across all parameters indicates effective mixing and suggests that the chains have reached equilibrium. This supports the model's statistical reliability and the robustness of the inferences that can be drawn about the factors influencing bike theft. Moreover, the visual consistency observed across different chains in each plot confirms that the posterior estimates are not sensitive to the initial values of the chains, further validating the model's findings.

@fig-rhat-plot displays the diagnostic, which assesses the convergence of Markov Chain Monte Carlo (MCMC) simulations for each parameter in the Bayesian logistic regression model. All $\hat{R}$ values are clustered around 1.00 and well below the critical thresholds of 1.05 or 1.1, indicating strong convergence across all parameters. This suggests that the multiple chains have mixed well and the posterior distributions are reliably estimated. As a result, the model's output can be trusted for further inference and analysis.

@@

For location-based predictors, thefts are significantly more likely to occur at Outdoor Premises with an OR of 1.51, and a credible interval from 1.01 to 2.26, indicating a clear increase in risk compared to other premises. Conversely, Residential Premises show an OR of 0.96, with a credible interval of 0.71 to 1.31, suggesting a slightly lower likelihood of thefts at these locations relative to others. The influence of Bike Cost per $1000 increase on theft likelihood is relatively neutral, with an OR nearly at 1 (0.99) and a credible interval between 0.78 and 1.27, indicating that the bike's cost does not significantly alter the odds of it being stolen.

@@

@fig-posterior-vs-prior shows a side-by-side comparison of prior and posterior distributions for each parameter in our Bayesian logistic regression model. This helps us see how initial assumptions (priors) change when we use real data (posteriors). For example, the shifts from priors to posteriors for parameters like the Occurrence Hour and Bike Cost show that the model makes significant adjustments based on the data it receives. These shifts are important because they tell us that the model is effectively updating its predictions to better match what's actually happening. Parameters like Occurrence Month and different premises types—like House, Other, and Outdoor—show varying levels of change, indicating their different impacts on the likelihood of bike theft. It shows that the model is capable of learning from the data, making it a reliable tool for understanding the factors that influence bike theft. This helps us trust the model more and use it to make better decisions or further analyses.

@@

## Summary of Findings {#sec-first-point}

In this paper, we conducted an in-depth analysis of bike theft data from Toronto using a Bayesian logistic regression model. The primary goal was to understand which factors most significantly affect the likelihood of a bike being stolen. To achieve this, we utilized data provided by the Toronto Police Service, focusing on several key variables such as the time of day, month, type of location (house, apartment, outdoors, or other), and the cost of the bike. The initial step involved cleaning and structuring the raw data to ensure it was suitable for analysis. We then built a Bayesian logistic regression model to estimate the probability of theft based on these different factors. This approach enabled us to uncover specific trends and identify high-risk areas for bike theft, providing valuable insights into the conditions under which thefts are most likely to occur. By understanding these patterns, we can propose targeted interventions to reduce bike thefts in the city.

Our data cleaning process involved dealing with missing values, reformatting categorical data, and aggregating certain location types to make the analysis more manageable and meaningful. We consolidated categories such as educational, commercial, and transit locations into a broader 'Other' category to ensure the model could focus on the primary types of locations where bikes are stored. This process was crucial for making the dataset more practical for analysis and helped improve the reliability of the conclusions drawn from the model. The Bayesian approach allowed us to incorporate prior knowledge into the analysis, which was particularly useful given the limitations in the dataset, such as the imbalance between theft and non-theft cases. Overall, our analysis provided a structured method to determine the impact of different environmental and temporal factors on bike theft.

## Understanding About the World

One of the key insights from this paper is that the type of location has a significant impact on the likelihood of bike theft. Our results showed that bikes parked outdoors are at a much higher risk of being stolen compared to those parked in residential areas like houses or apartments. This finding highlights the importance of location security in preventing bike theft. Public spaces, such as streets and parks, often lack adequate security measures, making them attractive targets for thieves. Therefore, to reduce the incidence of bike thefts, it is crucial to improve security measures in these outdoor areas. This could include installing more surveillance cameras, adding secure bike racks, and promoting the use of locks that are more difficult to break. Engaging local businesses and municipalities to create safer parking environments for cyclists could also play an important role in addressing this issue.

Another important insight from our analysis is the role of timing in bike theft. The data showed that bike thefts are more likely to occur in the afternoon and evening. This suggests that the risk of theft is higher during periods when people are more active and bikes are more likely to be left unattended for short periods, such as during errands or social visits. This insight is valuable because it helps to determine when theft prevention measures would be most effective. For example, increasing police patrols or community surveillance during these high-risk hours could help deter potential thieves. Additionally, public awareness campaigns could be launched to educate cyclists about the higher risk during these times, encouraging them to take extra precautions such as using better locks or parking in more secure locations. Understanding the temporal patterns of theft can also help city planners and law enforcement allocate resources more effectively to mitigate theft risks.

The analysis also revealed that the cost of the bike is a relevant factor, though its effect is more nuanced. While expensive bikes are valuable targets, mid-range bikes are also frequently stolen, possibly because they are easier to resell and less likely to have advanced security features. This suggests that theft prevention strategies should not only focus on high-end bikes but also on making security accessible and practical for all cyclists, regardless of the bike's value. Encouraging the use of multiple types of locks, offering secure parking areas, and subsidizing bike registration services are some of the strategies that could be employed to protect bikes across different price ranges.

### Limitations
While our analysis provides valuable insights, it is not without its limitations. One major weakness is the assumption that the relationship between predictors and the likelihood of theft is linear. This assumption may not fully capture the complexity of real-world factors that influence bike theft. In reality, there could be non-linear relationships or interactions between variables that our model does not account for. For example, the effect of bike cost might vary depending on the time of day or the type of location, indicating an interaction effect that our linear model cannot capture. Future studies could explore more sophisticated models, such as non-linear regression or machine learning approaches, to better capture these complex relationships.

Another limitation is that our dataset only includes reported bike thefts. This means that unreported cases, which could constitute a significant portion of all thefts, were not included in the analysis. The decision to report a theft may depend on various factors, such as the value of the bike, the perceived likelihood of recovery, or personal experiences with law enforcement. This reporting bias could lead to an incomplete picture of bike theft in Toronto, potentially skewing our findings. For example, lower-value bikes might be underrepresented in the data if owners feel it is not worth reporting their theft, even though these bikes are frequently targeted by thieves. Addressing this issue would require additional data collection efforts, such as surveys to estimate the number of unreported thefts.

Lastly, the model assumes independence between theft events, which may not always be the case. There could be clusters of thefts in certain areas or during specific times, suggesting that one theft might increase the likelihood of another nearby. This spatial and temporal correlation is not captured in our current model, which could lead to an underestimation of theft risk in certain hotspots. Including spatial analysis or temporal clustering in future models could provide a more comprehensive understanding of theft patterns and help in developing more targeted prevention strategies.

### Future Steps
There are still many questions left unanswered by our analysis, and there are several directions for future research that could help address these gaps. One area for further study is the inclusion of additional variables that might influence bike theft, such as the availability and quality of bike parking, neighborhood crime rates, and socioeconomic factors. Including these variables could provide a more detailed understanding of the contextual factors that contribute to theft risk. For example, neighborhoods with higher crime rates may see more bike thefts, and understanding these dynamics could help in tailoring interventions to specific areas.

Future research could also benefit from using more sophisticated models that consider potential non-linearities and interactions between variables. Machine learning models, such as decision trees or random forests, could be used to explore complex relationships in the data that are not well captured by traditional regression models. These approaches could help identify hidden patterns and provide more accurate predictions of theft risk under different conditions. Additionally, integrating spatial data and using geographic information system (GIS) tools could help identify hotspots for bike theft and provide insights into how environmental factors, such as proximity to public transit or major roads, affect theft risk.

Another important direction for future research is to gather more data on unreported thefts. Conducting surveys or working with community organizations to estimate the number of unreported thefts could provide a more complete picture of the true scale of the problem. This data could help address the reporting bias in our current analysis and lead to more accurate conclusions about the factors that influence bike theft. Additionally, partnerships with bike shops, community groups, and law enforcement could help in collecting richer data and implementing targeted interventions based on the findings.
